Scaling through abstractions – high-performance vectorial wave simulations for seismic inversion with Devito

### 2020-05-26 paper.tex
add reviews

@@

The output of the \devito compiler for the running example used in this
section is available at
\href{https://github.com/mloubout/SC20Paper/tree/master/codesamples}{CodeSample}
in \texttt{acou-so8.c}.

@@

@@

>>>>

\textcolor{red}{Wave-equation based geophysical inversion does not only require fast and accurate wave-equation sovers, 
but also adavnced algorithms for non-convex optimization for large scale PDE constraints inverse problem.
The high-level interface \devito provdes enables research and developement for these specific problem in a framework that scales
to industry size problem automatically through its compiler. Projects using \devito for the wave-equation solves include 
FWI \cite{witte2018alf}, compressived least-square RTM \cite{witte2018cls} or 
time-domain WRI \cite{rizzuti2020EAGEtwri, louboutin2020SEGtwri} that tackles the cycle-skipping issue in seismic inversion.}

@@

The output of the \devito compiler for the running example used in this
section is available at
\href{https://github.com/mloubout/SC20Paper/tree/master/codesamples}{CodeSample}
in \texttt{acou-so8.c} \textcolor{red}{and the accuracy of the generated code is verified through our
continuous integration pipeline against analytical solutions \cite{devito-api}.}

@@

\textcolor{red}{
\subsubsection{Strong scaling}
Strong scaling results from CX2.
}

@@

\textcolor{red}{One of the main challenges in gephysical exploration is to obtain access to reference implementations
of various wave-equations propagator. While we are in the prcess of comparing hand coded production code from high end contractor companies,
we here compare the performance to one of the few open source software available. It is extremely important to note that are not only 
interested in pure stencil framework, such as YASK \cite{yask}, that usually do no handle sparse operation for the source injection 
and receiver interpolation and are therefore nota dapted to measurement based inverse problems.}
